\documentclass[../omelveny-cv]{subfiles}

\begin{document}

%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Professional Experience}


\begin{cventries}

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %%% SF State Research - Math Education
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \cventry
    {Research Assistant - Math Curriculum Development}
    {San Francisco State University}
    {San Francisco, California}
    {Aug. 2022 - Current}
    {
        \begin{cvitems}
            \item {Work with Dr. Kimberly Seashore on developing an innovative curriculum for San Francisco State's Calculus I supplementary lab}
            \item {Adapt and develop labs that center group work while reinforcing core concepts in calculus}
        \end{cvitems}
    }

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %%% Stanford Youcubed
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \cventry
    {Technical Consultant and Developer}
    {Stanford University}
    {Palo Alto, California}
    {Jun. 2022 - Current}
    {
        \begin{cvitems}
            \item {Consult on the technical implementation on the curriculum of a data science class for high school students}
            \item {Develop code supporting and used by students in the data science course}
        \end{cvitems}
    }

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %%% SF State Research - Math Research
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \cventry
    {Research Assistant - Mathematical Research}
    {San Francisco State University}
    {San Francisco, California}
    {Aug. 2021 - Current}
    {
        \begin{cvitems}
            \item {Perform research under the guidance Dr. Dustin Ross on the relationship between tropical fans and the divisors of their Chow ring}
            \item {Supported by NSF RUI: Compacitfying moduli spaces of orbits, covers, and curves}
        \end{cvitems}
    }

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %%% SF State Teaching
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \cventry
    {Graduate Teaching Associate}
    {San Francisco State University}
    {San Francisco, California}
    {Aug. 2021 - Current}
    {
        \begin{cvitems}
            \item {Instructor of record for undergraduate precalculus and statistics classes}
        \end{cvitems}
    }

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %%% POSIT SCIENCE
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \cventry
    {Software Engineer}
    {Posit Science Corporation}
    {San Francisco, California}
    {Jan. 2017 - June 2021}
    {
        \begin{cvitems}
            \item {Developed software for the needs of multiple research studies on neuroplasticity}
            % \item {Work across the full software stack as a member of an Agile engineering team}
            \item {Maintained and extended data pipelines, allowing for efficient and secure access to clincal data}
            % \item {Design and implement front-end code for the web, iOS, and Android}
            \item {Developed back-end event scheduling systems and data models for efficient distributed computing}
            % \item {Optimized iOS development and build process by integrating modern build tools and methods}
            % \item {Formalized build and CI systems, reducing build errors and improving developer quality of life}
            % \item {Work with AWS remote servers; developed backup strategies to limit downtime in case of server failure}
            % \item {Helped develop a comprehensive test suite for web pages, reducing front-end bugs found by users}
        \end{cvitems}
    }

    %%%%%%%%%%%%
    % Old-position @ Posit
    %%%%%%%%%%%%
    \cventry
    {Research Associate \& Data Analyst}
    {Posit Science Corporation}
    {San Francisco, California}
    {Jul. 2015 - Jan. 2017}
    {
        \begin{cvitems}
            \item {Created in-house tools for automation of R\&D tasks; including study measure analytics, reporting dashboards, graphing tools and study-flow monitoring}
            \item {Performed exploratory data analysis for research studies and produced graphs and figures for publications}
            \item {Coordinated multi-site research trial, maintaining compliance with FDA regulations for Phase II clinical research}
            % \item {Built an extensible ETL pipeline allowing easier creation of complete data sets from multiple data stores, using a consistent and simple API}
            % \item {Led adoption of of Python and Jupyter notebooks among R\&D, leading to more automatable, reproducible, and shareable workflows}
            % \item {Aided in experimental design and planning of statistical analysis for studies}
            % \item {Managed remote teams of coordinators at collaborating institutions to insure data collection integrity and protocol adherence}
        \end{cvitems}
    }

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %%% VA/NCIRE
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \cventry
    {Research Associate II}
    {Northern California Institute for Research and Education}
    {San Francisco, California}
    {Mar. 2014 - Jul. 2015}
    {
        \begin{cvitems}
            \item {Coordinated and ran fMRI experiments exploring the relation of neurotransmitters and social cognition in schizophrenia}
            \item {Developed analysis pipelines for data collected in the course of fMRI and MEG experiments}
            % \item {Developed data processing pipeline for integration of fMRI images and behavioral data using Python}
            % \item {Made pipeline for processing MEG data using a combination of command line utilities, Python and MATLAB neuroimaging toolboxes}
            % \item {Established the back-end of a Microsoft Access DB as the main repository of study data, and migrated all previous study data stores}
            % \item {Analyzed data from experiments in Python and R and and produced graphs; produced figures for papers with matplotlib and ggplot2}
        \end{cvitems}
    }

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %%% SONOMA STATE
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \cventry
    {Instructional Student Assistant}
    {Sonoma State University}
    {Rohnert Park, California}
    {Sep. 2011 - Aug. 2013}
    {
        \begin{cvitems}
            \item {Tutored students in Music Theory I-IV, Music History, and Ear Training}
        \end{cvitems}
    }

\end{cventries}

\end{document}